Verifying Demonstrations

### 2018-02-25 paper/DistanceBounding.tex
Clarifies our need for the distance bounding

The majority of the existing \ac{DB} protocols are symmetric and thus requires 
an honest verifier.
There has been less work done in the domain of asymmetric (or public-key) 
\ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a 
\emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}.
More specifically, we must combine \ac{DB} with anonymous credentials, which we 
will describe next.

>>>>

The majority of the existing \ac{DB} protocols are symmetric and thus requires 
an honest verifier.
There has been less work done in the domain of asymmetric (or public-key) 
\ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a 
\emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with 
resistance to all the frauds mentioned above as well as against this verifier 
who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials, 
which we will describe next.
